The Form of Uncertainty Affects Selection for Social Learning

### 2023-02-26 ms.tex
updated ms

\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}. Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).

\paragraph{Acknowledgements.} We thank colleagues at the Cultural Evolution
Society and Cognitive Science Society annual meetings in 2022 who provided helpful feedback
to presentations of this work. We also thank the editor and two anonymous reviewers
for helping to improve to the original manuscript.%\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}
%

>>>>

\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}. Model and analysis code is
publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF
(\url{https://osf.io/t8exa/}). A guide to running the analyses is available on the GitHub repository.

\paragraph{Acknowledgements.} We thank colleagues at the Cultural Evolution
Society and Cognitive Science Society annual meetings in 2022 who provided helpful feedback
on presentations of this work. We also thank the editor and two anonymous reviewers
for helping to improve to the original manuscript.%\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}
%
